---
title: "main"
output: html_document
---

### Step 0: Specify directories 

```{r}
install.packages("matrixStats")
library(matrixStats)
library(tidyverse)
source("../lib/functions.R")

MS_train_dir <- "../data/Proj3_Data/MS_sample/data_train.csv"
MS_test_dir <- "../data/Proj3_Data/MS_sample/data_test.csv"
EM_train_dir <- "../data/Proj3_Data/eachmovie_sample/data_train.csv"
EM_test_dir <- "../data/Proj3_Data/eachmovie_sample/data_test.csv"
```

# Step 1: Read in data and transform the data into UI matrix.

```{r}
MS_train <- read.csv(MS_train_dir, as.is = TRUE, header = TRUE)
MS_train <- MS_train[, 2:4]

MS_UI_matrix <- MS_data_transform(MS_train)
save(MS_UI_matrix, file = "../output/MS_UI.RData")

EM_train <- read.csv(EM_train_dir, as.is = TRUE, header = TRUE)
EM_train <- EM_train[, 2:4]

EM_UI_matrix <- movie_data_transform(EM_train)
save(EM_UI_matrix, file = "../output/EM_UI.RData")

### EM ratings is in scale of 6. Create a normalized matrix in scale of 1 for Mean-squared difference sim weights calculation.
EM_UI_matrix_n <- EM_UI_matrix / 6

```

# Step 2: Model-based Algorithm

For EachMovie dataset

```{r}
system.time(results<-EM_for_CF(EM_UI_matrix,11))
save(results,file = "../output/EM_11.RData")
movie_EM_pred_11 <- movie_EM_pred(results$gamma_array,results$aic_assignment)
save(movie_EM_pred_11,file = "../output/movie_EM_pred_11.RData")
```

For Microsoft dataset

```{r}
system.time(results<-MS_for_CF(MS_UI_matrix,9))
save(results,file = "../output/MS_for_CF_9.RData")
MS_EM_pred_9 <- movie_EM_pred(results$gamma_array,results$aic_assignment)
save(MS_EM_pred_9,file = "../output/MS_EM_pred_9.RData")
```


# Step 3: Memory-based Algorithm

## Similarity Weights

Calculate similarity weights for EachMovie dataset.

```{r, warning = FALSE}
tm_pearson_EM <- NA
tm_spearman_EM <- NA
tm_cosine_EM <- NA
tm_entropy_EM <- NA
tm_msd_EM <- NA

tm_pearson_EM <- system.time(EM_sim_pearson <- calc_weight(EM_UI_matrix, method = 'pearson'))
tm_spearman_EM <- system.time(EM_sim_spearman <- calc_weight(EM_UI_matrix, method = 'spearman'))
tm_cosine_EM <- system.time(EM_sim_cosine <- calc_weight(EM_UI_matrix, method = 'cosine'))
# need to normalize EM_sim_entropy across rows
tm_entropy_EM <- system.time(EM_sim_entropy <- normalize_entropy(calc_weight(EM_UI_matrix, method = 'entropy')))
tm_msd_EM <- system.time(EM_sim_msd <- normalize_entropy(calc_weight(EM_UI_matrix, method = 'msd')))

tm_simr_EM <- system.time(EM_sim_simr <- calc_simrankpp_weight(EM_UI_matrix))

save(EM_sim_pearson, file = "../output/EM_sim_pearson.RData")
save(EM_sim_spearman, file = "../output/EM_sim_spearman.RData")
save(EM_sim_cosine, file = "../output/EM_sim_cosine.RData")
save(EM_sim_entropy, file = "../output/EM_sim_entropy.RData")
save(EM_sim_msd, file = "../output/EM_sim_msd.RData")
save(EM_sim_simr, file = "../output/EM_sim_simr.RData")

```

Report time used for calculating the weights.

```{r}
cat("For EachMovie Dataset: ")
cat("Time for Pearson Correlation =", tm_pearson_EM[1], "s \n")
cat("Time for Spearman Correlation =", tm_spearman_EM[1], "s \n")
cat("Time for Cosine Vector Similarity =", tm_cosine_EM[1], "s \n")
cat("Time for Mean-squared Difference =", tm_msd_EM[1], "s \n")
cat("Time for Entropy-based Method = ", tm_entropy_EM[1], "s \n")
cat("Time for SimRank Method = ", tm_simr_EM[1], "s \n")
```

Run Predictions

```{r}
EM_pred_pearson <- pred_matrix(EM_UI_matrix, EM_sim_pearson)
EM_pred_spearman <- pred_matrix(EM_UI_matrix, EM_sim_spearman)
EM_pred_cosine <- pred_matrix(EM_UI_matrix, EM_sim_cosine)
EM_pred_msd <- pred_matrix(EM_UI_matrix, EM_sim_msd)
EM_pred_entropy <- pred_matrix(EM_UI_matrix, EM_sim_entropy)
EM_pred_simr <- pred_matrix(EM_UI_matrix, EM_sim_simr)

save(EM_pred_pearson, file = "../output/EM_pred_pearson.RData")
save(EM_pred_spearman, file = "../output/EM_pred_spearman.RData")
save(EM_pred_cosine, file = "../output/EM_pred_cosine.RData")
save(EM_pred_entropy, file = "../output/EM_pred_entropy.RData")
save(EM_pred_msd, file = "../output/EM_pred_msd.RData")
save(EM_pred_simr, file = "../output/EM_pred_simr.RData")
```

Calculate similarity weights for Microsoft dataset.

```{r, warning = FALSE}
tm_pearson_MS <- NA
tm_spearman_MS <- NA
tm_cosine_MS <- NA
tm_entropy_MS <- NA
tm_msd_MS <- NA
tm_simrank_MS <- NA

tm_pearson_MS <- system.time(MS_sim_pearson <- calc_weight(MS_UI_matrix, method = 'pearson'))
tm_spearman_MS <- system.time(MS_sim_spearman <- calc_weight(MS_UI_matrix, method = 'spearman'))
tm_cosine_MS <- system.time(MS_sim_cosine <- calc_weight(MS_UI_matrix, method = 'cosine'))
tm_entropy_MS <- system.time(MS_sim_entropy <- normalize_entropy(calc_weight(MS_UI_matrix, method = 'entropy')))
tm_msd_MS <- system.time(MS_sim_msd <- normalize_entropy(calc_weight(MS_UI_matrix, method = 'msd')))
tm_simrank_MS <- system.time(MS_sim_simr <- calc_simrank_weight(MS_UI_matrix))

save(MS_sim_pearson, file = "../output/MS_sim_pearson.RData")
save(MS_sim_spearman, file = "../output/MS_sim_spearman.RData")
save(MS_sim_cosine, file = "../output/MS_sim_cosine.RData")
save(MS_sim_entropy, file = "../output/MS_sim_entropy.RData")
save(MS_sim_msd, file = "../output/MS_sim_msd.RData")
save(MS_sim_simr, file = "../output/MS_sim_simr.RData")
```

Report time used for calculating the weights.

```{r}
cat("For Microsoft Dataset: ")
cat("Time for Pearson Correlation =", tm_pearson_MS[1], "s \n")
cat("Time for Spearman Correlation =", tm_spearman_MS[1], "s \n")
cat("Time for Cosine Vector Similarity =", tm_cosine_MS[1], "s \n")
cat("Time for Mean-squared Difference =", tm_msd_MS[1], "s \n")
cat("Time for Entropy-based Method = ", tm_entropy_MS[1], "s \n")
cat("Time for SimRank Method = ", tm_simrank_MS[1], "s \n")
```

Run Predictions

```{r}
MS_pred_pearson <- pred_matrix(MS_UI_matrix, MS_sim_pearson)
MS_pred_spearman <- pred_matrix(MS_UI_matrix, MS_sim_spearman)
MS_pred_cosine <- pred_matrix(MS_UI_matrix, MS_sim_cosine)
MS_pred_msd <- pred_matrix(MS_UI_matrix, MS_sim_msd)
MS_pred_entropy <- pred_matrix(MS_UI_matrix, MS_sim_entropy)
MS_pred_simr <- pred_matrix(MS_UI_matrix, MS_sim_simr)

save(MS_pred_pearson, file = "../output/MS_pred_pearson.RData")
save(MS_pred_spearman, file = "../output/MS_pred_spearman.RData")
save(MS_pred_cosine, file = "../output/MS_pred_cosine.RData")
save(MS_pred_entropy, file = "../output/MS_pred_entropy.RData")
save(MS_pred_msd, file = "../output/MS_pred_msd.RData")
save(MS_pred_simr, file = "../output/MS_pred_simr.RData")
```


### Step 4: Evaluating Predictions.

Load in test data.
```{r}
MS_test <- read.csv(MS_test_dir, as.is = TRUE, header = TRUE)
MS_test <- MS_test[, 2:4]

MS_UI_matrix_test <- MS_data_transform(MS_test)
save(MS_UI_matrix_test, file = "../output/MS_UI_test.RData")

EM_test <- read.csv(EM_test_dir, as.is = TRUE, header = TRUE)
EM_test <- EM_test[, 2:4]

EM_UI_matrix_test <- movie_data_transform(EM_test)
save(EM_UI_matrix_test, file = "../output/EM_UI_test.RData")

source("../lib/evaluation.R")
```

Ranked Scores.


```{r}
MS_rs_pearson <- rank_scoring(MS_pred, MS_UI_matrix_test, 5)
MS_rs_spearman <- rank_scoring(MS_pred_spearman, MS_UI_matrix_test, 5)
MS_rs_cosine <- rank_scoring(MS_pred_cosine, MS_UI_matrix_test, 5)
MS_rs_msd <- rank_scoring(MS_pred_msd, MS_UI_matrix_test, 5)
MS_rs_entropy <- rank_scoring(MS_pred_entropy, MS_UI_matrix_test, 5)
MS_rs_simr <- rank_scoring(MS_pred_simr, MS_UI_matrix_test, 5)

EM_rs_pearson <- rank_scoring(EM_pred_pearson, EM_UI_matrix_test, 5)
EM_rs_spearman <- rank_scoring(EM_pred_spearman, EM_UI_matrix_test, 5)
EM_rs_cosine <- rank_scoring(EM_pred_cosine, EM_UI_matrix_test, 5)
EM_rs_msd <- rank_scoring(EM_pred_msd, EM_UI_matrix_test, 5)
EM_rs_entropy <- rank_scoring(EM_pred_entropy, EM_UI_matrix_test, 5)
EM_rs_simr <- rank_scoring(EM_pred_simr, EM_UI_matrix_test, 5)

```

MAE.

```{r}
MS_mae_pearson <- eva_mae(MS_pred_pearson, MS_UI_matrix_test)
MS_mae_spearman <- eva_mae(MS_pred_spearman, MS_UI_matrix_test)
MS_mae_cosine <- eva_mae(MS_pred_cosine, MS_UI_matrix_test)
MS_mae_msd <- eva_mae(MS_pred_msd, MS_UI_matrix_test)
MS_mae_entropy <- eva_mae(MS_pred_entropy, MS_UI_matrix_test)
MS_mae_simr <- eva_mae(MS_pred_simr, MS_UI_matrix_test)

EM_mae_pearson <- eva_mae(EM_pred_pearson, EM_UI_matrix_test)
EM_mae_spearman <- eva_mae(EM_pred_spearman, EM_UI_matrix_test)
EM_mae_cosine <- eva_mae(EM_pred_cosine, EM_UI_matrix_test)
EM_mae_msd <- eva_mae(EM_pred_msd, EM_UI_matrix_test)
EM_mae_entropy <- eva_mae(EM_pred_entropy, EM_UI_matrix_test)
EM_mae_simr <- eva_mae(EM_pred_simr, EM_UI_matrix_test)

```

RMSE.

```{r}
MS_rmse_pearson <- eva_rmse(MS_pred_pearson, MS_UI_matrix_test)
MS_rmse_spearman <- eva_rmse(MS_pred_spearman, MS_UI_matrix_test)
MS_rmse_cosine <- eva_rmse(MS_pred_cosine, MS_UI_matrix_test)
MS_rmse_msd <- eva_rmse(MS_pred_msd, MS_UI_matrix_test)
MS_rmse_entropy <- eva_rmse(MS_pred_entropy, MS_UI_matrix_test)
MS_rmse_simr <- eva_rmse(MS_pred_simr, MS_UI_matrix_test)

EM_rmse_pearson <- eva_rmse(EM_pred_pearson, EM_UI_matrix_test)
EM_rmse_spearman <- eva_rmse(EM_pred_spearman, EM_UI_matrix_test)
EM_rmse_cosine <- eva_rmse(EM_pred_cosine, EM_UI_matrix_test)
EM_rmse_msd <- eva_rmse(EM_pred_msd, EM_UI_matrix_test)
EM_rmse_entropy <- eva_rmse(EM_pred_entropy, EM_UI_matrix_test)
EM_rmse_simr <- eva_rmse(EM_pred_simr, EM_UI_matrix_test)
```

### Step 5: Neighborhood selection on Pearson Similarity Weights.

## Step 5.1: Load matrices of similarity weights
```{r}
#for MS data
load("../output/MS_sim_pearson.RData")
load("../output/EM_sim_pearson.RData")
load("../output/MS_UI.RData")
load("../output/EM_UI.RData")
load("../output/MS_pred_pearson.RData")
load("../output/EM_pred_pearson.RData")
load("../output/MS_UI_test.RData")
load("../output/EM_UI_test.RData")
dim(MS_sim)
dim(movie_sim)
```

```{r}
install.packages("Metrics")
install.packages("caret")
```

```{r}
library(Metrics)
library(caret)
```


## Step 5.2: Filtering the data by minimum threshold only

# a. MS: Select neighbors by setting minimum threshold for MS weights to 0.1, 0.2, 0.3, 0.4, and 0.5.

Any weights that are less than the minimum threshold are set to 0.
```{r}
MS_corr0.1 <- matrix(MS_sim_pearson, ncol = dim(MS_sim_pearson)[1])
MS_corr0.1[abs(MS_corr0.1) < 0.1] <- 0

MS_corr0.2 <- matrix(MS_sim_pearson, ncol = dim(MS_sim_pearson)[1])
MS_corr0.2[abs(MS_corr0.2) < 0.2] <- 0

MS_corr0.3 <- matrix(MS_sim_pearson, ncol = dim(MS_sim_pearson)[1])
MS_corr0.3[abs(MS_corr0.3) < 0.3] <- 0

MS_corr0.4 <- matrix(MS_sim_pearson, ncol = dim(MS_sim_pearson)[1])
MS_corr0.4[abs(MS_corr0.4) < 0.4] <- 0

MS_corr0.5 <- matrix(MS_sim_pearson, ncol = dim(MS_sim_pearson)[1])
MS_corr0.5[abs(MS_corr0.5) < 0.5] <- 0
```

# b. movie: Select neighbors by setting minimum threshold for movie weights to 0.1, 0.2, 0.3, 0.4, and 0.5.

Any weights that are less than the minimum threshold are set to 0.
```{r}
movie_corr0.1 <- matrix(EM_sim_pearson, ncol = dim(EM_sim_pearson)[1])
movie_corr0.1[abs(movie_corr0.1) < 0.1] <- 0

movie_corr0.2 <- matrix(EM_sim_pearson, ncol = dim(EM_sim_pearson)[1])
movie_corr0.2[abs(movie_corr0.2) < 0.2] <- 0

movie_corr0.3 <- matrix(EM_sim_pearson, ncol = dim(EM_sim_pearson)[1])
movie_corr0.3[abs(movie_corr0.3) < 0.3] <- 0

movie_corr0.4 <- matrix(EM_sim_pearson, ncol = dim(EM_sim_pearson)[1])
movie_corr0.4[abs(movie_corr0.4) < 0.4] <- 0

movie_corr0.5 <- matrix(EM_sim_pearson, ncol = dim(EM_sim_pearson)[1])
movie_corr0.5[abs(movie_corr0.5) < 0.5] <- 0
```


## Step 5.3: Filtering the data by minimum threshold and setting the number of closest neighbors to an absolute value 

# a. Function to return the position of the n largest values of matrix m, column p. We will use these indices to eventually filter out anything that is not the top n highest correlated users.

```{r}
nlargest <- function(m, n, p) {
  res <- order(m[p, ], decreasing = TRUE)[seq_len(n)];
  pos <- arrayInd(res, dim(m), useNames = TRUE);
  return(pos)
}
```

# b. MS: selecting 20 top correlated neighbors and 40 top correlated neighbors
```{r}
# 20 neighbors
MS_corr0.1_nnbors20 <- matrix(MS_sim_pearson, ncol = dim(MS_sim_pearson)[1])
MS_corr0.1_nnbors20[abs(MS_corr0.1_nnbors20) < 0.1] <- 0

#temporarily set the diagonals to NA while we find highest correlations; otherwise, the highest correlated in any row will be 1.
diag(MS_corr0.1_nnbors20) <- NA
test <- matrix(0, ncol = dim(MS_sim_pearson)[1], nrow = dim(MS_sim_pearson)[1])

for (i in 1:ncol(MS_corr0.1_nnbors20)){
  temp <- nlargest(MS_corr0.1_nnbors20, 20, i)[, 1]
  test[temp, i] <- MS_corr0.1_nnbors20[temp, i]
}

#set the diagonals back to 1
diag(test) <- 1
MS_corr0.1_nnbors20 <- test



# 40 neighbors
MS_corr0.1_nnbors40 <- matrix(MS_sim_pearson, ncol = dim(MS_sim_pearson)[1])
MS_corr0.1_nnbors40[abs(MS_corr0.1_nnbors40) < 0.1] <- 0

#temporarily set the diagonals to NA while we find highest correlations; otherwise, the highest correlated in any row will be 1.
diag(MS_corr0.1_nnbors40) <- NA
test <- matrix(0, ncol = dim(MS_sim_pearson)[1], nrow = dim(MS_sim_pearson)[1])

for (i in 1:ncol(MS_corr0.1_nnbors40)){
  temp <- nlargest(MS_corr0.1_nnbors40, 40, i)[, 1]
  test[temp, i] <- MS_corr0.1_nnbors40[temp, i]
}

#set the diagonals back to 1
diag(test) <- 1
MS_corr0.1_nnbors40 <- test
```

# c. movie: selecting 20 top correlated neighbors and 40 top correlated neighbors
```{r}
# 20 neighbors
movie_corr0.1_nnbors20 <- matrix(EM_sim_pearson, ncol = dim(EM_sim_pearson)[1])
movie_corr0.1_nnbors20[abs(movie_corr0.1_nnbors20) < 0.1] <- 0

#temporarily set the diagonals to NA while we find highest correlations; otherwise, the highest correlated in any row will be 1.
diag(movie_corr0.1_nnbors20) <- NA
test <- matrix(0, ncol = dim(EM_sim_pearson)[1], nrow = dim(EM_sim_pearson)[1])

for (i in 1:ncol(movie_corr0.1_nnbors20)){
  temp <- nlargest(movie_corr0.1_nnbors20, 20, i)[, 1]
  test[temp, i] <- movie_corr0.1_nnbors20[temp, i]
}

#set the diagonals back to 1
diag(test) <- 1
movie_corr0.1_nnbors20 <- test



# 40 neighbors
movie_corr0.1_nnbors40 <- matrix(EM_sim_pearson, ncol = dim(EM_sim_pearson)[1])
movie_corr0.1_nnbors40[abs(movie_corr0.1_nnbors40) < 0.1] <- 0

#temporarily set the diagonals to NA while we find highest correlations; otherwise, the highest correlated in any row will be 1.
diag(movie_corr0.1_nnbors40) <- NA
test <- matrix(0, ncol = dim(EM_sim_pearson)[1], nrow = dim(EM_sim_pearson)[1])

for (i in 1:ncol(movie_corr0.1_nnbors40)){
  temp <- nlargest(movie_corr0.1_nnbors40, 40, i)[, 1]
  test[temp, i] <- movie_corr0.1_nnbors40[temp, i]
}

#set the diagonals back to 1
diag(test) <- 1
movie_corr0.1_nnbors40 <- test
```

## Step 5.4: Get the prediction matrix for all filtered datasets
```{r}
source("../lib/functions.R")
```

# a. MS
```{r}
MS_corr0.1_pred <- pred_matrix(MS_UI_matrix, MS_corr0.1)
MS_corr0.2_pred <- pred_matrix(MS_UI_matrix, MS_corr0.2)
MS_corr0.3_pred <- pred_matrix(MS_UI_matrix, MS_corr0.3)
MS_corr0.4_pred <- pred_matrix(MS_UI_matrix, MS_corr0.4)
MS_corr0.5_pred <- pred_matrix(MS_UI_matrix, MS_corr0.5)
MS_corr0.1_nnbors20_pred <- pred_matrix(MS_UI_matrix, MS_corr0.1_nnbors20)
MS_corr0.1_nnbors40_pred <- pred_matrix(MS_UI_matrix, MS_corr0.1_nnbors40)
```

# b. movie
```{r}
movie_corr0.1_pred <- pred_matrix(EM_UI_matrix, movie_corr0.1)
movie_corr0.2_pred <- pred_matrix(EM_UI_matrix, movie_corr0.2)
movie_corr0.3_pred <- pred_matrix(EM_UI_matrix, movie_corr0.3)
movie_corr0.4_pred <- pred_matrix(EM_UI_matrix, movie_corr0.4)
movie_corr0.5_pred <- pred_matrix(EM_UI_matrix, movie_corr0.5)
movie_corr0.1_nnbors20_pred <- pred_matrix(EM_UI_matrix, movie_corr0.1_nnbors20)
movie_corr0.1_nnbors40_pred <- pred_matrix(EM_UI_matrix, movie_corr0.1_nnbors40)
```

## Step 5.5: Get the MAE for the different neighborhood selections
```{r}
source("../lib/evaluation.R")
```

# a. MS
```{r}
MSmae <- c(eva_mae(MS_corr0.1_pred, MS_UI), eva_mae(MS_corr0.2_pred, MS_UI), eva_mae(MS_corr0.3_pred, MS_UI), eva_mae(MS_corr0.4_pred, MS_UI), eva_mae(MS_corr0.5_pred, MS_UI), eva_mae(MS_corr0.1_nnbors20_pred, MS_UI), eva_mae(MS_corr0.1_nnbors40_pred, MS_UI))

MSmae
```

# b. movie
```{r, warning = FALSE}
moviemae <- c(eva_mae(movie_corr0.1_pred, movie_UI_test), eva_mae(movie_corr0.2_pred, movie_UI_test), eva_mae(movie_corr0.3_pred, movie_UI_test), eva_mae(movie_corr0.4_pred, movie_UI_test), eva_mae(movie_corr0.5_pred, movie_UI_test), eva_mae(movie_corr0.1_nnbors20_pred, movie_UI_test), eva_mae(movie_corr0.1_nnbors40_pred, movie_UI_test))

moviemae
```

## Step 5.6: Calculate RMSE for the different neighborhood selections

# a. MS
```{r}
MSrmse <- c(eva_rmse(MS_corr0.1_pred, MS_UI_matrix_test), eva_rmse(MS_corr0.2_pred, MS_UI_matrix_test), eva_rmse(MS_corr0.3_pred, MS_UI_matrix_test), eva_rmse(MS_corr0.4_pred, MS_UI_matrix_test), eva_rmse(MS_corr0.5_pred, MS_UI_matrix_test), eva_rmse(MS_corr0.1_nnbors20_pred, MS_UI_matrix_test), eva_rmse(MS_corr0.1_nnbors40_pred, MS_UI_matrix_test))

MSrmse
```

# b. movie
```{r, warning = FALSE}
moviermse <- c(eva_rmse(movie_corr0.1_pred, movie_UI_test), eva_rmse(movie_corr0.2_pred, movie_UI_test), eva_rmse(movie_corr0.3_pred, movie_UI_test), eva_rmse(movie_corr0.4_pred, movie_UI_test), eva_rmse(movie_corr0.5_pred, movie_UI_test), eva_rmse(movie_corr0.1_nnbors20_pred, movie_UI_test), eva_rmse(movie_corr0.1_nnbors40_pred, movie_UI_test))

moviermse
```

## Step 5.7: Generate relevant figures and tables
```{r}
library(data.table)

MSres <- data.frame(MSmae, MSrmse)
names(MSres)[1] <- "MAE"
names(MSres)[2] <- "RMSE"
setattr(MSres, "row.names", c("Min Abs Corr = 0.1", "Min Abs Corr = 0.2", "Min Abs Corr = 0.3", "Min Abs Corr = 0.4", "Min Abs Corr = 0.5", "Min Abs Corr = 0.1, NNbors = 20", "Min Abs Corr = 0.1, NNbors = 40"))

movieres <- data.frame(moviemae, moviermse)
names(movieres)[1] <- "MAE"
names(movieres)[2] <- "RMSE"
setattr(movieres, "row.names", c("Min Abs Corr = 0.1", "Min Abs Corr = 0.2", "Min Abs Corr = 0.3", "Min Abs Corr = 0.4", "Min Abs Corr = 0.5", "Min Abs Corr = 0.1, NNbors = 20", "Min Abs Corr = 0.1, NNbors = 40"))
```


